---
title: "MTB Utrechtse Heuvelrug 2016"
author: "M. Klein"
date: "10-1-2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("leaflet")
library("rjson")
library("plyr")
library("dplyr")
library("googleway")
library("lubridate")
```

## MTB Tracks Utrechtse Heuvelrug 2016
### The MTB app shows the capability of:
- shiny
- plotly
- leaflet

## The data and functionality
- data on the rides is extracted from Strava
- leaflet with 7 MTB tracks on the Utrechtse Heuvelrug, The Netherlands
- interactive plotly's of rides per month, day and hour
- prediction of number of rides in the coming days

##Location
The application is published on shinyapps.io

URL: https://nielknetraam.shinyapps.io/MUH2016/
```{r, echo = FALSE}
json_file <- "MUH2016/data/track.json"
tracks <- fromJSON(file=json_file)
tracksdf <- do.call("rbind.fill", lapply(tracks$data, as.data.frame))
tracksdf <- tracksdf %>% mutate(name = as.character(name), color = as.character(color), polyline = as.character(polyline)) %>% filter(id != 8, type == "permanent")

renderLeaflet({
    muh <- leaflet() %>% setView(lng = 5.40759, lat = 52.01522, zoom = 11) %>% addTiles()
    for (i in 1:nrow(tracksdf)) {
        decode_track <- decode_pl(tracksdf[i,]$polyline)
        muh <- muh %>% addPolylines(lng=decode_track$lon, lat=decode_track$lat, color = tracksdf[i,]$color, popup = tracksdf[i,]$name)
    }
    muh <- muh %>% addLegend(position = "bottomleft", labels=tracksdf$name, colors=tracksdf$color)
    muh
})
```

##Totals
The table contains the total number of rides in 2016 per track

```{r, echo=FALSE}
names <-c("Rhenen","","","","","","Kwintelooijen","","", "", "","Amerongen","","","","Hoge Ginkel","","","","","","","Leersum","Zeist","","","","","","Austerlitz")
sectorDaily <- read.csv("MUH2016/data/SectorAggregate.csv", sep=";")
sectorDaily <- sectorDaily %>% 
    filter(dmy(date) <= ymd("2016-12-31")) %>%
    mutate(date=dmy(date),
           time=ymd_h(paste(date,hour)),
           name = names[id],
           weekday = weekdays(date))
sectorDaily %>% group_by(name) %>% summarise(count=sum(count))

```





